Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-09-11 concurrency/CPP 2024/paper.tex
clean up todos

\section{Conclusion and Future Work}
Concurrent search structure templates are a promising approach for proving the correctness of concurrency patterns and data structures separately, and then combining them to obtain verified concurrent data structures. We have translated the approach to apply to C programs using VST, with appropriate imperative versions of the key \lstinline{traverse} functions that define the templates, and used it to prove the correctness of an (appropriately refactored) existing concurrent data structure. However, the translation also exposed some ambiguities and limitations in the approach: for instance, the \lstinline{inRange} function of the give-up template must either be assumed to exist in the data structure or incorporated into the template, and the \lstinline{delete} operation of binary search trees does not decompose naturally into a concurrent part and a data-structure-specific part.  %\wm{Do we have an idea of how to fix this?}
The next step is to implement templates as a truly generic framework, with proofs of \lstinline{traverse}, etc. that can be freely combined with verified sequential data structures via a clear interface that defines the functions a data structure must provide and the assumptions the template makes on them.
Ultimately, we hope to use the template approach to verify data structures such as Masstree~\cite{masstree} and Wormhole~\cite{wormhole}, complicated real-world search structures that combine multiple concurrency patterns for maximum performance on multicore architectures.

>>>>

\section{Conclusion and Future Work}
Concurrent search structure templates are a promising approach for proving the correctness of concurrency patterns and data structures separately, and then combining them to obtain verified concurrent data structures. We have translated the approach to apply to C programs using VST, with appropriate imperative versions of the key \lstinline{traverse} functions that define the templates, and used it to prove the correctness of an (appropriately refactored) existing concurrent data structure. However, the translation also exposed some ambiguities and limitations in the approach: for instance, the \lstinline{inRange} function of the give-up template must either be assumed to exist in the data structure or incorporated into the template, and the \lstinline{delete} operation of binary search trees does not decompose naturally into a concurrent part and a data-structure-specific part.  %\wm{Do we have an idea of how to fix this?}
The next step is to implement templates as a truly generic framework, with proofs of \lstinline{traverse}, etc. that can be freely combined with verified sequential data structures via a clear interface that defines the functions a data structure must provide and the assumptions the template makes on them (e.g., by verifying template functions with respect to a data-structure typeclass).
Ultimately, we hope to use the template approach to verify data structures such as Masstree~\cite{masstree} and Wormhole~\cite{wormhole}, complicated real-world search structures that combine multiple concurrency patterns for maximum performance on multicore architectures.
